Paper Title*

### 2018-12-26 paper.tex
add datasheet reference
link budget

\subsection{Spreading Factor}
\par Spreading factor (SF) is the ratio between symbol rate and chip rate. The ratio between symbol and chip rate is equal to $2$\textsuperscript{SF}. SF can take values between 7 to 12. [CITE] SF also determines data rate of a LoRa transmission.

@@

Where SF is spreading factor $SF \in \{7,..,12\}$, CR is error correction code rate $CR \in \{1,..,4\}$ and BW is bandwidth in Hertz. [CITE:modulation basics]

@@

\section{Simulation Environment} \label{Simulation Environment}
[TODO] A discrete event simulator is implemented in Python to simulate LoRa network performance. https://github.com/tugrulyatagan/simlorafs

\begin{table}
\centering
\caption{Gateway Sensitivity for different SFs}
\label{table:gw_sf_sensitivity}
\begin{tabular}{|c|c|c|c|c|c|c|c|}
\hline
            &         & \multicolumn{6}{c|}{\textbf{SF}}        \\ \cline{3-8} 
            &         &    7 &    8 &    9 &   10 &   11 &   12 \\ \hline
            & 125 kHz & -123 & -126 & -129 & -132 & -133 & -136 \\ 
\textbf{BW} & 250 kHz & -120 & -123 & -125 & -128 & -130 & -133 \\
            & 500 kHz & -116 & -119 & -122 & -125 & -128 & -130 \\
\hline
\end{tabular}
\end{table}
[CITE:datasheet]

\begin{equation} \label{eq:rx_sensitivity}
P^{dBm}
\end{equation}
[CITE:modulation basics]

\subsection{Link Model}
[TODO]

>>>>

\subsection{Spreading Factor}
\par Spreading factor (SF) is the ratio between symbol rate and chip rate. The ratio between symbol and chip rate is equal to $2$\textsuperscript{SF}. SF can take values between 7 to 12. SF also determines data rate of a LoRa transmission \cite{AN1200.22}.

@@

Where, SF is spreading factor $SF \in \{7,..,12\}$, CR is error correction code rate $CR \in \{1,..,4\}$ and $BW$ is bandwidth in Hertz \cite{AN1200.22}.

@@

\section{Simulation Environment} \label{Simulation Environment}
\par [TODO] A discrete event simulator is implemented in Python to simulate LoRa network performance. https://github.com/tugrulyatagan/simlorafs

\subsection{Link Model}
\par [TODO]

The link budget of a wireless system or network is a measure of all the gains and losses from the
transmitter, through the propagation channel, to the target receiver. These gains and losses include
system gains and losses associated with the antenna, matching networks, etc. as well as losses
associated propagation channel itself (either though modelling or measured data).
Typically randomly varying channel mechanisms such as multipath and Doppler fading are taken into
account by factoring additional margin depending on the anticipated severity.
The link budget of a network wireless link can be expressed as:

\begin{equation} \label{eq:rx_sensitivity}
P^{dBm}_{RX} = P^{dBm}_{TX} + G^{dB}_{SYS} - L^{dB}_{SYS} - L^{dB}_{PATH}
\end{equation}

Where, $P^{dBm}_{RX}$ is the expected receive power at the receiver. $P^{dBm}_{TX}$ is the transmit power. $G^{dB}_{SYS}$ is the system gains such as transmitter and receiver antenna gain. $L^{dB}_{SYS}$ is the system losses such as transmitter and receiver line, circuit, antenna losses. $L^{dB}_{PATH}$ is the propagation path loss between transmitter and receiver antennas.

\par Receive sensitivity of a LoRa gateway for different SFs and BWs can be found in Table \ref{table:gw_sf_sensitivity} \cite{SX1276}.

\begin{table}
\centering
\caption{Gateway Sensitivity for different SFs}
\label{table:gw_sf_sensitivity}
\begin{tabular}{|c|c|c|c|c|c|c|c|}
\hline
            &         & \multicolumn{6}{c|}{\textbf{SF}}        \\ \cline{3-8} 
            &         &    7 &    8 &    9 &   10 &   11 &   12 \\ \hline
            & 125 kHz & -123 & -126 & -129 & -132 & -133 & -136 \\ 
\textbf{BW} & 250 kHz & -120 & -123 & -125 & -128 & -130 & -133 \\
            & 500 kHz & -116 & -119 & -122 & -125 & -128 & -130 \\
\hline
\end{tabular}
\end{table}
